Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
new task graphs

\vspace{-.2in}
\begin{center}
\begin{abstract}
\noindent This investigation is motivated by the increasing significance of the usability of systems in today's competitive technology market. Usability testing and usability evaluations have become important tools in the assessment of user interfaces. This paper presents empirical mobile usability studies of two distinct map applications: Google Maps and Apple Maps. Participants of this investigation were asked to carry out three tasks with each mobile application. The results of this examination include (a) the contextual factors studied; (b) the core usability metrics measured; (c) quantitative data collected from each task; and (d) a brief qualitative review from each participant. This paper not only presents the usability metrics collected by the study but also presents a heuristic evaluation of each map application.
\end{abstract}
\end{center}

@@

\subsection{Results}
\textit{The design of system icons is simple, modern, friendly, and sometimes quirky. Each icon is reduced to its minimal form, with every idea edited to its essence. The designs ensure readability and clarity even at small sizes}
\begin{figure}[ht]
\includegraphics[keepaspectratio, width=1\textwidth ]{task1.pdf}
\end{figure}

>>>>

\vspace{-.2in}
\begin{center}
\begin{abstract}
\noindent This investigation is motivated by the increasing significance of the usability of systems in today's competitive technology market. Usability testing and usability evaluations have become important tools in the assessment of user interfaces. This paper presents empirical mobile usability studies of two distinct map applications: Google Maps and Apple Maps. Participants of this investigation were asked to carry out three tasks with each mobile application. The results of this examination include (a) the contextual factors studied; (b) quantitative data collected from each task; (c) a brief qualitative review from each participant; and (d) the core usability metrics measured. This paper not only presents the usability metrics collected by the study but also presents a heuristic evaluation of each map application.
\end{abstract}
\end{center}

@@

\subsection{Results}
\textit{The design of system icons is simple, modern, friendly, and sometimes quirky. Each icon is reduced to its minimal form, with every idea edited to its essence. The designs ensure readability and clarity even at small sizes}
\begin{figure}[ht]
\includegraphics[keepaspectratio, width=1\textwidth ]{task1.pdf}
\end{figure}
\begin{figure}[ht]
\includegraphics[keepaspectratio, width=1\textwidth ]{task2.pdf}
\end{figure}
\begin{figure}[ht]
\includegraphics[keepaspectratio, width=1\textwidth ]{task3.pdf}
\end{figure}
